hormones

### 2019-10-24 analysis/07_hormones.Rmd
confirming correlations between hormone and gene expression

>>>>

# do control bird with high prolactin hormone have high PRL expression in the pituitary? yes.

```{r PRLvPRL}
PRLpit <- read_csv("../results/10_PRLpit.csv") %>% 
  filter(treatment == "control") %>% 
  arrange(desc(PRL))
head(PRLpit,2)
```

```{r}
prolactin <- read_excel("../results/Pigeon prolactin concentrations juil 2018.xlsx", sheet = 1)  %>% 
            filter(Treatment == "baseline")  %>% 
            select(ColorBands,BandNo_old, Treatment, Sex, `Prolactin ng/mL`)  %>% 
            arrange(desc(`Prolactin ng/mL`))

head(prolactin,2)
```
